   \datedexperience{Futurewei Technologies}{2013-Present /Santa Clara, CA, USA} 
    \explanation{Principal Engineer}
  \explanationdetail{%\coloredbullet\ %

 Working with the office of the CTO, involved in the industry research on next-generation network technologies and protocols in service provider and large-scale network markets. Day to day work involves equal parts research, standardization and collaboration. It entails presenting, meeting partners and customers explaining new research directions, design and solution with technical details.\\

 \newcommand{\extraone}{%
 \textbf{Technical Research:} Focus on in-network services and capabilities for emerging applications in industry automation, and advanced media ('holographic type' and high-precision communications). Analyse challenges in current networks and research new data plane and packet format mechanisms. Designing proof-of-concepts for research in transport and network layer. Earlier, \textbf{a:} developed a virtual routing architecture and protocol for auto-provisioning of tenant networks. \textbf{b:} An end to end 5G/B5G Network Slicing architecture and  protocol for resource sharing in a multi-domain, multi-tenant network. \textbf{c:} Co-innovated preferred path routing for 5G and B5G backhaul.
  }
    \newcommand{\extratwo}{%
   \textbf{Standards activities}: Founding member of FG-NET-2030. \emph{Network 2030 initiative} at ITU, to develop formal road map and requirements for the next-gen network technologies. Familiar with IETF mechanisms and leading standardization of network slices in IETF.}

    \newcommand{\extrathree}{%

    \textbf{Program and Project Management}: Both in the US and Europe on future network architecture topics, guiding students on New IP research.
    }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    \createbullets{\listofextras}
}

%------------------------------------------------
