   \datedexperience {Cisco Systems} {2005-2013/Milpitas, USA} 
    \explanation{Technical Leader }
  \explanationdetail{%\coloredbullet\ %

 \\ Led many projects on IOS-XR, IOS for edge service routers such as  Openflow agent, policy based routing, Lawful intercept and platform bring up. I learnt a great deal about the scalability challenges and means to overcome them in a distributed operating system such as IOS-XR. 
 \\ At Cisco, I have contributed to many aspects - bringing up new WAN, LAN line cards, and implementing  metro Ethernet design. I mentored new hires, resolved customer issues and worked with  platform-hardware and core operating system teams.

 \newcommand{\extraone}{%
 \textbf{Policy services layer} Developed architecture to support flow-based infrastructure as well as network programmability (ONEP) for a distributed system.  \textbf{Platform Stability}: Provided HA solution for lawful intercept as a part of L2L3 services team. Developed hybrid architecture endian aware message translation methods.}

 \newcommand{\extratwo}{%
 \textbf{Edge router (7600) services}: developed platform-dependent slow-path forwarding module, added performance tweaks for QoS, selectively drop packets, prioritizing control packets, and bug fixes. }

 \newcommand{\extrathree}{%
 \textbf{L2 functions}: Designed support for CFM 802.1ag standard over EoMPLS and different Metro Ethernet services. The services included CFM over VFI interfaces.
 }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    \createbullets{\listofextras}
}
 %------------------------------------------------
